%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Jo}{Kroese}

\position{Statistical consultant and data scientist}
\address{Amsterdam, Netherlands}

\mobile{+44 7804 479 238}
\email{\href{mailto:jo@jokroese.com}{\nolinkurl{jo@jokroese.com}}}
\homepage{jokroese.com}
\linkedin{jokroese}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I am a data scientist who believes data can help us build a world
that is more joyful and just. I have worked in a diverse range of areas,
from calculating the number of fish caught in the sea for the UK
government to founding a citizen-centred research organisation.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {October 2021}
    {Jo Kroese~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{work}{%
\section{Work}\label{work}}

\begin{cventries}
    \cventry{Statistical Consultant and Founder}{The Open Consultancy}{Amsterdam, Netherlands}{2018 - Present}{\begin{cvitems}
\item Consult for a range of large international organisations including FSC, the UK government, DEFRA, Sport England and UEFA.
\item Redesigned the UK's analysis of how much fish is caught, saving the government over half a million pounds each year.
\item Designed FSC's risk score system, estimating the risk of almost one hundred thousand forestry projects.
\end{cvitems}}
    \cventry{Associate Researcher}{Substance}{Manchester, England}{2018 - Present}{\begin{cvitems}
\item Collaborate on national projects in health and environment policy.
\end{cvitems}}
    \cventry{Founder}{Radical Data}{Amsterdam, Netherlands}{2019 - Present}{\begin{cvitems}
\item Run a research organisation focused on how data science can be used as a tool for citizen empowerment through art, activism and policy.
\item Supported by a research grant from Stimuleringsfonds, Netherlands.
\item Spoken internationally, from lectures at Edinburgh University and Université de Montréal to public talks at Mozilla Festival and Digital Arts Zurich.
\end{cvitems}}
    \cventry{Musician}{Jobi}{Amsterdam, Netherlands}{2019 - Present}{\begin{cvitems}
\item Perform live coded dance music internationally, from Amsterdam to Medellín, Colombia.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Mathematics, MMath (Hons) ∙ First Class}{University of Manchester}{Manchester, England}{2013 - 2018}{\begin{cvitems}
\item Integrated masters degree with focus on applied maths, statistics and computer science
\item Masters dissertation on `Network Models of Political Repression and Revolution'
\end{cvitems}}
    \cventry{Mathematics, Exchange Year}{McGill University}{Montréal, Canada}{2016 - 2017}{\begin{cvitems}
\item Courses studied include graduate courses in economics, mathematics and computer science
\end{cvitems}}
\end{cventries}

\hypertarget{selected-software-development}{%
\section{Selected software
development}\label{selected-software-development}}

\begin{cvhonors}
    \cvhonor{}{\textbf{\href{https://joekroese.github.io/tidymrp/}{tidymrp}}: Author \newline Easy-to-run multilevel regression and poststratification (MRP) analyses in R.}{}{2021\newline}
    \cvhonor{}{\textbf{\href{https://joekroese.github.io/tidymine/}{tidymine}}: Author \newline Robust variable selection.}{}{2020\newline}
    \cvhonor{}{\textbf{\href{https://tiddlyroam.org}{tiddlyroam}}: Author \newline Open source software to create your own personal wikipedia that has been downloaded over 20,000 times.}{}{2020\newline}
\end{cvhonors}

\hypertarget{languages}{%
\section{Languages}\label{languages}}

English ∙ French ∙ Dutch

\hypertarget{references}{%
\section{References}\label{references}}

\begin{cvhonors}
    \cvhonor{}{\textbf{\href{https://www.cefas.co.uk/about-us/people/kieran-hyder/}{Dr Kieran Hyder}}: Principal Scientist, Cefas.}{}{}
    \cvhonor{}{\textbf{\href{https://www.substance.net/team/gavin-mellor/}{Dr Gavin Mellor}}: Director and Head of Data and Consultancy, Substance.}{}{}
\end{cvhonors}

\end{document}
